### 2014-11-12 tex/evaluation.tex
Updated results table.
Updated results table with state counts.

\begin{table} [h]
  \centering
  \begin{tabular}{| c | c | r | r | r | r | }
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{2}{|c|}{Time} &\multicolumn{2}{|c|}{ Paths }\\
								&	&\gsetxt{}	&SH	&\gsetxt{} & SH\\
   \hline
    \multirow{3}{*}{LinkedList }&3	& 0.91 & 0.69  &1656 & 25		 \\
   		 				& 4	& 2.92 & 0.91	&17485  & 39 \\
   						& 5	& 20.8 & 1.59 &232743 & 56\\
						& 6	& 283 & 2.36		&3731094 & 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree } & 1	&0.26	& 0.36 & 6	 & 6\\
   		 				& 2	& 0.83 & 0.93	& 143 & 33\\
   						& 3	& 20.6 & 4.03 & 515 & 328\\
    \hline
      \multirow{3}{*}{TreeMap}&1	 & 0.47 & 0.77 &11 & 11 \\
   		 				&2	& 8.99 & 4.72	& 127 & 73 \\
   						& 3	& - & 146	& - & 887 \\

    \hline
  \end{tabular}
  \caption{test results}
  \label{tab:results}
\end{table}

@@

As expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}. By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth. Remarkably, path growth in the k-bound appears to be sub-linear.

>>>>

\begin{figure*}[t]
%\begin{table} [t]
  \centering
  \begin{tabular}{| c | c | r | r | r | r | r | r | r | r | r |}
  \hline
   \multirow{2}{*}{Method }&\multirow{2}{*}{ $k$ }
   &\multicolumn{3}{|c|}{Time} &\multicolumn{3}{|c|}{States} &\multicolumn{3}{|c|}{ Paths }\\
								&	&\gsetxt{} & LS		&SH		&\gsetxt{}	& LS & SH&\gsetxt{}	& LS & SH\\
   \hline
    \multirow{3}{*}{LinkedList }			&3	& 0.91	& 1.21	& 0.69	& 2465	& 2844	& 99		&1656	& 1269	& 25\\
   		 						& 4	& 2.92	& 3.35	& 0.91	& 25774	& 29977	& 155	&17485	& 13550	& 39\\
   								& 5	& 20.78	& 19.47	& 1.59	& 341164	& 400296	& 223	&232743	& 181849	& 56\\
								& 6	& 280.56	& 299.19	& 2.36	&5447980	&6437201	& 303	&3731094	&2933027	& 76\\
    \hline
    \multirow{3}{*}{BinarySearchTree }	& 1	& 0.26	& 0.28	& 0.36	& 19		& 23		& 29		& 6		& 6		& 6\\
   		 						& 2	& 0.83	& 1.28	& 0.93	& 143	& 143	& 145	& 43		& 42		& 33\\
   								& 3	& 20.63	& 25.55	& 4.03	& 1953	& 1703	& 1485	& 515	& 515	& 328\\
    \hline
      \multirow{3}{*}{TreeMap}			& 1	& 0.47	& 0.52	& 0.77	& 65		& 70		& 215	& 11		& 11		& 11\\
   		 						& 2	& 8.99	& 9.73	& 4.72	& 1009	& 942	& 3219	& 127	& 122	& 73\\
   								& 3	& -		& -		& 145.56	& -		& -		& 78695	& -		& -		& 887\\

    \hline
  \end{tabular}
  \caption{test results}
  \label{tab:results}
%\end{table}
\end{figure*}

@@

The results ofAs expected, the repeated use of lazy initialization throughout the program causes an exponential increase in the number of paths explored by \gsetxt{}. By combining many of the \gsetxt{} paths, \symtxt{} avoids the exponential path explosion, demonstrating dramatically reduced, though still exponential, execution time growth. Remarkably, path growth in the k-bound appears to be sub-linear.
